\chapter{Introduction}
\par{The demand for efficient and adaptable enterprise solutions has never been greater in today's
rapidly evolving technological landscape. Within the South African context, where the
intersection of academia and industry holds significant promise for innovation and economic
growth, the exploration of novel approaches to software development becomes imperative. This
introduction outlines the rationale, objectives, and structure of the research study aimed at
investigating the feasibility and efficacy of leveraging university student talent to develop a
commercial-grade software solution in the form of an Enterprise Resource Planning (ERP)
system in collaboration with TaskFlow a partnering North-West University-industry software
development company.}

\par{Collaboration between industry and academia is essential to benefit the global technological
village \citep{baig2018bridging}. Unfortunately, universities, especially in developing nations, often lack the resources to allow for the proper development of skills needed by students entering the software development workforce. Through collaborative initiatives, software companies possess
the necessary skills, know-how, and technology to improve the skills of university students in a
controlled environment that simulates real-world experience. For instance, companies
specialising in software development, like TaskFlow, integrate solutions such as Contact Centre,
Customer Relations Management, Dialer, and Helpdesk into a comprehensive Enterprise
Resource Planning (ERP) suite. This empowers their clients to optimise time and make
informed business decisions through tailor-made and integrated software that more efficiently
and effectively streamlines their entire business processes.}

\par{Integrated ERP systems significantly affect the organisation's value chain in both primary and secondary operations \citep{amini2020erp}. By connecting business and management
activities, enterprise resource planning (ERP) assists organisations in realising their full potential \citep{uccakturk2013effects}. Additionally, while ERP systems are pivotal to operational
success, the associated expenses of non-integrated software solutions present significant barriers
to cost and scalability. Consequently, many software-developing companies aim to minimise the
cost of training interns on the theory behind and use of integrated software tools, project management, and software development, especially when developing complex systems such as ERP suits. This research aims to investigate whether Higher Education Institutions (HEIs) can effectively address the current challenges faced by the industry by introducing collaborative
university/industry-applied teaching to some postgraduate computer science and information
systems curricula. By doing so, the study explores the viability of creating a mutually beneficial
relationship between academia and industry, which can bring positive outcomes for both parties and students. As such, the research will delve into the potential of the curricula in Project management and System development at Honor's level to mitigate the challenges faced by the
industry while nurturing a dynamic and symbiotic partnership between academia and industry.}

\section{Problem Statement}
\par{The intersection of academia and industry presents unique opportunities and formidable
challenges. Employers find it challenging to locate people with the knowledge and abilities
needed for open positions \citep{barnett2011partnering}. Former President Barack Obama thus emphasised the need for lawmakers and national higher education associations to urge educational institutions to not only set ambitious educational attainment targets but also ensure that their goals address the current gap in required industry skills \cite{barnett2011partnering}. Thus, creating an educational environment for efficient learning and skill development is imperative to provide the correct skills for industry \citep{baig2018bridging}. Therefore, it is beneficial for graduate students to comprehend how the industry operates and how idea and innovation are turned into the products and services society requires \citep{foley1997technology}.}
\par{The central inquiry for this study emerges from the argument that tertiary education students
need to be trained for the requirements of a professional workspace \citep{baig2018bridging}. The
question arises: \textit{To what extent can postgraduate students be effectively taught to
develop industry-standard software solutions such as ERP systems amidst the multidimensional challenges of technical proficiency, client satisfaction, and academic rigour?}}

\section{Research Aims and Objectives}
\par{The upcoming study will concentrate on three primary objectives. First, it will define the essential components and prerequisites of a fully functional, versatile, and industry-approved software system. Secondly, it aims to pinpoint the critical abilities that students must possess to create an acceptable software system in the industry. Lastly, it will explore the roles of academia and industry in facilitating the successful creation of such a system through sound project management and system development skills.}
\par{This study aims to evaluate the feasibility of creating a commercially viable software solution in
collaboration with a software development company as part of the NWU computer science and information systems department's prescribed curriculum on IT project management and software development honours program. Through collaboration with the industry, this study aims to showcase the technical abilities of computer science students by developing a software solution that meets commercial standards. This initiative also seeks to equip students with the necessary skills to become valuable contributors to the South African workforce. The project aims to conduct a pilot study to identify the key success factors in guiding postgraduate students at a Higher Education Institution (HEI) in an underdeveloped country. The goal is to provide these students with industry exposure in a formalised academic and learning environment, enabling them to develop economically viable software. The study seeks to determine how the students can be effectively mentored and trained and what support and resources are necessary to ensure their success.
Ultimately, the findings of this study will be used to inform the design of future programs that seek to foster innovation and economic growth in underdeveloped regions of the world.}
\par{This study explores the possibility of integrating projects and software development techniques taught in an educational setting by teaching existing structures and practices of a typical software development company in the South African industry. The objective is, therefore, to teach computer science and information systems graduates to identify market opportunities and, by applying industry practices and sound PM and SD methods, to develop software products that are commercially viable and aligned with market demands. As such, the research seeks to uncover optimal practices and tactics that improve educational insights regarding the teaching of PM and software development procedures, integrating cutting-edge best practices from the industry. To assess the software solution's viability as a marketable product, the research will conclude through an extensive evaluation by proficient experts and professionals in the software development industry. It will also involve thoroughly examining the client's satisfaction and feedback after receiving the final system, including any concerns they may raise. This
assessment will determine the critical success factors in developing commercial software, the roles of industry and academia in the learning process, and any necessary improvements to enhance the learning experience.}

\section{Hypothesis}
\par{Postgraduate computer science and information systems students can build a sophisticated software solution that is commercially viable, such as an ERP system when partnering with the expertise and resources of industry partners.}

\section{Methods of Investigation}
\par{Throughout the commencement of the research, the study will draw upon two main facets to substantiate the claims made in the paper's conclusions: the vast amount of academic literacy available and the other experiment based data collection processes referring to the development project as the main experiment. Both of these will be outlined below to provide clarity on both matters.}
\subsection{Literature Study}
\par{To enhance the credibility, accuracy, and validity of the study, a thorough and systematic review of pertinent literature will be conducted. This will involve targeting keywords such as higher education, academia, ERP systems, software success, project management, system implementation, and commercialisation. Research will be prioritised from a positivist perspective and examine peer-reviewed articles from reliable sources such as the NWU Library, Google Scholar, IEEE Xplore, and ACM Digital Library. In addition, grey literature from trusted sources like white papers and industry reports will be considered, as this research incorporates best practices from the industry. Duplicate articles or those not meeting our eligibility criteria will not be accepted. To locate important material, references from key papers will be scrutinised and analysed for citation patterns, thus seeking advice and insights from
subject matter experts. The focus will be on resources published between 2015 and 2024 to ensure relevance. Historical research to be focused on include:}
\par{\begin{itemize}
    \item Njanka, S. Q., Sandula, G., and Colomo-Palacios, R. (2021). It-business alignment: A
systematic literature review. Procedia Computer Science, 181:333–340.
    \item Kenge, R. and Khan, Z. (2020). A research study on the erp system implementation and
current trends in erp. Shanlax International Journal of Management, 8(2):34–39.
    \item Guo Chao Alex, P. and Chirag, G. o. C. I. S. (2014). Cloud erp: a new dilemma to modern
organisations? Journal of Computer Information Systems, 54(4):22–30.
    \item Bagchi-Sen, S., Baines, N., and Smith, H. L. (2022). Characteristics and outputs of univer-
sity spin-offs in the united kingdom. International Regional Science Review, 45(6):606–
635.
\end{itemize}}
\subsection{Methods of Investigation}
\par{As mentioned earlier, this study aims to thoroughly examine the literature on software systems and student development of software in developed nations to identify applicable lessons for developing environments like South Africa. A key objective is to equip students with the knowledge needed in PM and system development to create software that adheres to industry best practices. To achieve this, the study will assess the business case for higher educational institutions to develop commercially viable software for the industry as potential clients. Once
the need is established, the next step will be identifying the technological and functional requirements for creating software that real-world clients can use to support their daily operations. Once the software is completed, the study will evaluate the usability of the software as well as the learning experience and the proficiency of postgraduate students in applying project management and systems development methodologies to complex software development. The aim is to offer significant and insightful knowledge that can be utilised by higher education institutions (HEIs) in underdeveloped countries to improve the functionality, efficiency, and acceptance of their software and systems development projects. This will help HEIs teach the most relevant and useful theories of project management and teamwork, ultimately enhancing their students employability and marketability in the industry.}
\par{As such, the researcher will serve as an integral part of the project, overseeing software development. As mentioned, according to set project management milestones, the software system will undergo testing by reviewers with experience in the information technology and ERP industries. All lessons learned and the input from reviewers will be compiled to produce a workable framework that can direct HEIs in leveraging project management and software development curricula to develop commercially viable software solutions and systems for internal and industry applications.}

\section{Chapter Division}
\par{This thesis is structured into six main chapters, each meticulously crafted to delve into specific
facets of the research endeavour, elucidating methodologies, literature insights, empirical findings, and concluding reflections. The chapters are as follows:}
\par{The Research Design chapter serves as the foundational cornerstone of the thesis, this chapter
provides a detailed exposition of the research methodology and paradigm guiding the study. Adopting a design science research methodology and a positivist paradigm, this section navigates the theoretical underpinnings of the research approach, outlining its epistemological and ontological foundations. Through meticulous delineation of research
methods, including data collection techniques, sampling strategies, and analytical frameworks, this chapter lays the groundwork for subsequent empirical inquiry. Once this chapter has concluded, a review of the current literature in the field will be done to pinpoint previous scientific findings that will benefit the current study.}
\par{The Literature Study chapter embarks on an immersive journey through the annals of academic literature, traversing diverse domains ranging from ERP systems to implementation frameworks. The section unfolds with a lucid articulation of the problem statement, contextualising the research within the broader academic discourse. Subsequent sections delve into the intricacies of ERP systems, exploring their architectural nuances, functional capabilities, and strategic significance within organisational contexts. Furthermore, the chapter probes into the value chain framework, dissecting the interconnected dynamics of people, processes, and technology in driving organisational success. Anchored by comprehensive reviews of commercialization strategies, software implementation frameworks, and the role of students in industry, this chapter serves as a beacon of scholarly inquiry, illuminating the theoretical landscape underpinning the research endeavor. Once the theoretical landscape has been illuminated, a case study can be conducted to generate findings regarding the research question, and help the research endeavour edge closer to final conclusion.}
\par{The Case Study embarks on a voyage of empirical exploration, this chapter unfurls the intricacies of the case study conducted within the hallowed confines of TaskFlow. With a keen focus on project design and execution, this section unveils the methodological blueprint guiding the project life cycle. Through an exhaustive examination of project management methodologies, agile development frameworks, and strategic planning processes, this chapter offers unparalleled insights into the operational dynamics underpinning software development endeavours. Furthermore, by delineating the project pipeline and process, this section charts the trajectory of the project's evolution, elucidating key milestones, challenges encountered, and lessons learned along the way. Once the case study has concluded, and sufficient data is collected around the subject at hand, an expert reviewer will reveal the depth of the truth within the findings and help the project reach its final conclusion.}
\par{In pursuit of academic rigour and scholarly validation, the Expert Reviewer chapter invites the discerning gaze of domain experts to scrutinise the research methodology and findings. Through structured interviews, expert assessments, and critical appraisals, this section seeks to engender a dialectic discourse, fostering intellectual exchange and epistemic enrichment. By subjecting the research endeavour to rigorous scrutiny, this chapter endeavours to enhance the robustness and validity of the research findings, ensuring their salience and applicability within the broader academic community. The chapter that follows will discuss the results that were found throughout the study.}
\par{The Results and Discussion serves as the crucible of empirical inquiry, this chapter presents and analyses the empirical findings gleaned from the case study and expert review. Through meticulous data analysis techniques, including qualitative coding, thematic analysis, and comparative synthesis, this section unveils the rich tapestry of insights garnered from the research endeavour. Furthermore, by fostering a dialectic discourse between empirical findings and theoretical frameworks, this chapter endeavours to unravel the underlying mechanisms and causal relationships shaping the research phenomena. The chapter that follows will make the final conclusions regarding the total study and its findings; it will act as a summary for the research project and summarise the findings to draw the final conclusion.}
\par{The conclusions chapter aims to synthesise key insights, implications, and avenues for future research, this chapter offers a reflective denouement to the research endeavour. Through a judicious synthesis of empirical findings and theoretical frameworks, this section distils the essence of the research inquiry, elucidating its broader implications and relevance within academic and practical contexts. Furthermore, by delineating avenues for future research and scholarly inquiry, this chapter seeks to catalyse intellectual curiosity and foster a culture of continuous learning and innovation.}
\par{In summation, this research endeavour represents a concerted effort to bridge the gap between academic theory and industrial practice, laying the foundation for the subsequent chapter, "Research Design." By elucidating the theoretical underpinnings and methodological frameworks guiding the study, the forthcoming chapter endeavors to translate lofty aspirations into tangible research methodologies, fostering innovation, collaboration, and economic prosperity within the South African software development landscape.}